---
title: "Effect of smoking on FEV"
author: "Amy Willis"
date: "11/29/2019"
output: 
    pdf_document:
        number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Here is where I would introduce the study and provide motivation, etc.

## Summary statistics

Here are some summary statistics for the older participants in the FEV study:

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hold'}
library(tidyverse)
fev <- read_csv("datasets/fev.csv")
library(knitr)
library(kableExtra)
```

```{r, echo=FALSE}
fev %>%
  filter(age > 16) %>%
  rename(`Age (years)` = age) %>%
  mutate(Sex = ifelse(sex == 1, "Male", "Female")) %>%
  mutate(Smoker = ifelse(smoke == 1, "Yes", "No")) %>%
  group_by(`Age (years)`, Sex, Smoker) %>%
  summarise("Sample size" = n(), 
            "Mean FEV (L)" = mean(fev) %>% round(2)) %>%
  kable %>%
  kable_styling(full_width = F,  
                bootstrap_options = c("bordered","striped")) %>%
  column_spec(1, border_left = T) %>%
  column_spec(3, border_right = T) %>%
  column_spec(5, bold = T, border_right = T) 
```

# Data analysis

Here is a plot:

```{r, echo=FALSE, fig.height=3, fig.width=5, fig.align='center'}
fev %>%
  filter(age < 18 & age > 9) %>%
  mutate(sex = as.character(sex),
         smoke = as.character(smoke),
         age = as.factor(age)) %>%
  ggplot(aes(x = age, y = fev, col = smoke)) +
  geom_boxplot() + theme_bw()
```

Notice how there is no code shown in the pdf version of this document... but you can see it in the Rmd file. That was done by setting `echo=FALSE` in the code chunks that created the table and the figure.  